\documentclass{article}

\title{MY 5 PROGRAMMING LANGUAGES}
\date{November 2021}
\author{Peter Ebubechukwu Olele}

\begin{document}
	\section{Python}
	Founder - Guido van Rossum,
	History:
	Van Rossum created Python while in the Netherlands (National Research Institute for Mathematics and Computer Science) to be a successor to the language “ABC”. 
	It began to be implemented in late 1989. 
	Rossum worked as the head of the Python project up until July 2018
	In 1994, Python 1.0 was released with features such as Lambda, Map and Exception handling
	Python 2.0 in 2000 brought comprehension of lists as well as Garbage Collection System
	Python 3.0 was released officially in December of 2008
	Versions 2.x and 3.x are the most used.\\
	
	Python can be used for:
	\begin{itemize}
		\item Game development
		\item Desktop GUI applications
		\item Language development\\
	\end{itemize}

    Available Integrated Development Environment (IDEs):
	\begin{itemize}
	 \item Sublime text
	 \item Visual Studio Code
	 \item Atom
    \end{itemize}    
    
    
    \section{C++}
    Founder: Bjarne Stroustrup. History:
    Bjarne Stroustrup created C++ to be an “extension”  to the programming language “C”. Development for the language started in 1982, 3 years prior to the development of its predecessor C. He was motivated by his PhD thesis to create it.\\
    
    C++ can be used for:
	\begin{itemize}
	\item Web browsers
	\item Databases
	\item IoT Devices
	\item Tools for machine learning
	\item Augmented/Virtual reality applications
	\item Scientific research and development\\
	\end{itemize}  
    
    Available Integrated Development Environment (IDEs):
	\begin{itemize}
	\item C++ Builder
	\item Kite
	\item Virtual Code Studio
	\item Atom
	\item eMacs\\
	\end{itemize}   
    
    \section{JavaScript}
    Founder: Brendan Eich. History:
    Netscape employee Brendan Eich created the language within 10 days. It started out under the name ‘Mocha’ in September of 1995 but was soon later changed to JavaScript after being called LiveScript for a brief while.
    The language was designed for the then newly formed Mozilla Firefox.
    It became ECMA standard in 1997.\\
    
    JavaScript can be used for:
	\begin{itemize}
	 \item Creating responsive web pages 
	 \item Application production
	 \item Web Server Creation
	 \item Game production\\
    \end{itemize} 

    Available Integrated Development Environment (IDEs):
   \begin{itemize}
	\item Eclipse
	\item Atom
	\item Web Storm
	\item Visual Studio Code
	\item NetBeans\\
   \end{itemize}


   \section{HyperText Markup Language (HTML)}
   Founder: Tim Berners-Lee. History:
   It was first publicly made available in 1991 but was only in 1995 released officially. 
   It was created to provide accessible information via Web browsers.
   HTML was given international standards status in 2000 with the production of HTML 5 starting in 2004 with standardisation 10 years later.\\
   
   HTML can be used for:
   \begin{itemize}
	\item Navigating the internet 
	\item Game production
	\item Support for Data entry\\
   \end{itemize}    

   Available Integrated Development Environment (IDEs):
   \begin{itemize}
	\item Codelobster
	\item Atom
	\item Web Storm
	\item Adobe Dreamweaver
	\item Komodo Edit\\
   \end{itemize}


	\section{HyperText Preprocessor (PHP)}
	Founder: Rasmus Lerdorf. History:
	Lerdorf wrote some code in the programming language C to manage his web homepage in 1994.
	He created PHP by extending the code to work with databases.
	It was originally established to create simple applications on web.
	Version 8.0, established in November 26, 2020, is the latest version.\\
	
   PHP can be used for:
   \begin{itemize}
	\item Communicating with the web server
	\item Creation of login pages
	\item Creation of cookies
	\item Form handling
	\item Email transfer\\
   \end{itemize}	
	
   Available Integrated Development Environment (IDEs):
   \begin{itemize}
	\item Codelobster
	\item Atom
	\item Web Storm
	\item Adobe Dreamweaver
	\item Komodo Edit\\
   \end{itemize}
	
	
	
	
	

\end{document}